---
title: "Weight of Fish"
author: "Sandra Iovino"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

if(!require("Bolstad")) {install.packages("Bolstad");require("Bolstad")}
```
## Perch

### Best Models

```{r}
perchmodel=lm(Weight~ ., data=Perch)
summary.lm(perchmodel)

```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
 
  The best variables to predict weight is H and W because H is height and w is width.     
 
### Best Two regressor model
```{r}
perch2=lm(Weight~Height+Width,data=Perch)
summary.lm(perch2)
```
The best 2 regressor model is to predict weight using Height and Width.    

## Pike

### Best Models
```{r}
pikemodel=lm(Weight~ ., data=Pike)
summary.lm(pikemodel)

```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
  The best variables to predict weight is Length1 and Length3.    

### Best Two regressor model
```{r}
pike2=lm(Weight~Length1+Length3,data=Pike)
summary.lm(pike2)
```

The best 2 regressor model to help predict Weight is Length 1 and Length 3.  

## Roach

### Best Models
```{r}
roachmodel=lm(Weight~ ., data=Roach)
summary.lm(roachmodel)

```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
 
 The best variables to predict weight is Length3 and Width.      


### Best Two regressor model
```{r}
roach2=lm(Weight~Length3+Width,data=Roach)
summary.lm(roach2)
```

The best 2 regressor model to help predict Weight is Length 3 and Width.  

## Final Summary Statements

When trying to figure out what the best way to find out Height for Perch is Height and Width.   

When trying to figure out what the best way to find out Height for Pike is Length 1 and Length 3.  

When trying to figure out what the best way to find out Height for Roach is Length 3 and Width.  